Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-31 msbr_reproc.tex
grammar

In this work only Zone I unit cell with 0.132 volume fraction of fuel 
considered, neutron spectrum for Zone II cell where salt fraction is 37\% 
should be harder and the peak in thermal energy region predicted to be much 
lower. To obtain high fidelity neutron energy spectrum whole \gls{MSBR} core 
analysis is required.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The depletion calculation of the \gls{MSBR} unit cell model for finding the 
equilibrium states was performed using the Serpent 2 Monte Carlo code to 
simulate simplified case of the online reprocessing and refueling to find 
equilibrium material composition. When running depletion calculation, the 
fission products are removed and fertile/fissile materials are added to fuel 
salt every 3 days. The important MSR feature, online reprocessing I\& refueling 
is implemented in the Serpent 2 material burnup routine. The results of this 
study indicate that from the depletion calculation the multiplication factor 
slowly decreases and reaches to the equilibrium state. The most obvious finding 
to emerge from the analysis of initial and equilibrium materials composition is 
that neutron energy spectrum is harder for equilibrium state because 
significant amount of heavy fission products were accumulated in the \gls{MSBR} 
core.

>>>>

In this work, only the Zone I unit cell, where the fuel salt volume fraction is 
13.2\%, was considered. The neutron spectrum for Zone II cell, where the fuel 
salt volume fraction is 37\% is expected to be harder and the peak in thermal 
energy region is predicted to be much 
lower. To obtain a high-fidelity neutron energy spectrum, a full-core \gls{MSBR}
analysis is required.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The depletion calculation of the \gls{MSBR} unit cell model for finding the 
equilibrium states was performed using the Serpent 2 Monte Carlo code to 
simulate simplified case of the online reprocessing and refueling to find 
equilibrium material composition. When running depletion calculation, the 
fission products are removed and fertile/fissile materials are added to fuel 
salt every 3 days. The important MSR feature, online reprocessing I\& refueling 
is implemented in the Serpent 2 material burnup routine. The results of this 
study indicate that from the depletion calculation the multiplication factor 
slowly decreases and reaches to the equilibrium state. The most obvious finding 
to emerge from the analysis of initial and equilibrium materials composition is 
that neutron energy spectrum is harder for equilibrium state because 
significant amount of heavy fission products were accumulated in the \gls{MSBR} 
core.
